Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

We now solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-1}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-1)$-SJ has an input size at most $n$, and let us represent its result as $\J(R_1, ..., R_{k-1}, H', V)$. We prove in Appendix~\ref{app:hv}:

\begin{lemma} \label{lmm:hv:type2:recur-output}
    $|\J(R_1, ..., R_{k-1}, H', V)| \le \out$.
\end{lemma}

@@

\extraspacing {\bf Generating $\bm{\J^*}$.}

>>>>

We now solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-3}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-1)$-SJ has an input size at most $n$, and let us represent its result as $\J(R_1, ..., R_{k-3}, H', V)$. We prove in Appendix~\ref{app:hv}:

\begin{lemma} \label{lmm:hv:type2:recur-output}
    $|\J(R_1, ..., R_{k-3}, H', V)| \le \out$.
\end{lemma}

@@

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h, v)$.
